---
title: "[regimes](http://anderwilson.github.io/regimes/)"
output:
  html_document:
    css: style.css
    theme: cerulean
    highlight: tango
    includes:
      after_body: doc_suffix.html
---


## REGression In Multivariate Exposure Settings
[Ander Wilson](http://anderwilson.github.io/)

### Overview

The **regimes** R packages contains regression methods for estimating the relationship between a multivariate exposure and an outcome. The package is oriented toward environmental health and environmental epidemiology research but is applicable in a variety of settings. 


### Installation

The **regimes** package can be installed using **devtools**.
```{r, message=FALSE, warning=FALSE, eval=FALSE}
library(devtools)
devtools::install_github(repo="AnderWilson/regimes")
library(regimes)
```

Note: You may need to install the [**graph**](http://bioconductor.org/packages/release/bioc/html/graph.html) and [**Rgraphviz**](http://bioconductor.org/packages/release/bioc/html/Rgraphviz.html) packages from [Bioconductor](http://bioconductor.org).



- Alternates if you do not have openMP (Mac users) 
```{r install-regimes-2, eval=FALSE}
devtools::install_github("AnderWilson/regimes",
                         ref="noopenmp")
```

- Or install from Mac binary after downloading [`regimes_0.5.11.tgz`](https://github.com/AnderWilson/regimes/blob/gh-pages/regimes_0.5.11.tgz)
```{r install-regimes-3, eval=FALSE}
install.packages("regimes_0.5.11.tgz", 
    repos = NULL, type = .Platform$pkgType)
```

### Methods

[acpme](http://anderwilson.github.io/regimes/acpme.html): adjustment for confounding in the presence of multivariate exposures

[bdlim](http://anderwilson.github.io/regimes/bdlim.html): Bayesian distributed lag interaction models
